Evaluate PEER in each cohort and brain region

### 2021-03-15 combined_analysis/eval_resid_in_each.Rmd
upload correct cell type

    PEER_setPhenoMean(model, t(geneExpr[,i,]))

    # PEER_setNmax_iterations(model, 2)
    PEER_setNk(model,50)

    # upload observed expression
    file = paste0('geneExpr_',gsub(" ", '', gsub("-", "_", datID)), '_', CT,".RDS")
    storeData( geneExpr, file, paste0(datID, " Observed expression", ' - ', CT))

    # upload covariate matrix
    file = paste0('covariateMatrix_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( cov_matrix, file, paste0(datID, " Covariates for QTL analysis", ' - ' , CT))

    # upload latent variables
    file = paste0('PEER_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis", ' - ', CT))
  }
}
```

>>>>

    # fit PEER
    # model = PEER()

    # PEER_setPhenoMean(model, t(geneExpr[,i,]))

    # PEER_setCovariates(model, cov_matrix)

    # # PEER_setNmax_iterations(model, 2)
    # PEER_setNk(model,50)

    # PEER_update(model)

    # extract PEER latent variables
    # first ncol(cov_matrix) columns are the oringal covariates
    # latentVariables = PEER_getX(model)[,-c(1:ncol(cov_matrix))]
    # rownames(latentVariables) = rownames(cov_matrix)
    # colnames(latentVariables) = paste0("PEER_", 1:ncol(latentVariables))

    # upload observed expression
    file = paste0('geneExpr_',gsub(" ", '', gsub("-", "_", datID)), '_', CT,".RDS")
    storeData( geneExpr[,i,], file, paste0(datID, " Observed expression", ' - ', CT))

    # # upload covariate matrix
    # file = paste0('covariateMatrix_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    # storeData( cov_matrix, file, paste0(datID, " Covariates for QTL analysis", ' - ' , CT))

    # # upload latent variables
    # file = paste0('PEER_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    # storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis", ' - ', CT))
  }
}
```
